microscopy Data Clean

### 2020-08-06 Microscopy Data Clean.Rmd
updated t-tests

#now I have to do some t-tests, since I used the same cultures for mono and co for each replicate, paired t-tests are allowed.
##### 
#I know this sucks, but it's 1 AM so idgaf
SaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)
SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)

PaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
PaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
PaWtAggTest<-t.test(x = PaMonoWtAggSum, y = PaCoWtAggSum, paired = T)
PaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
PaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
PaMutAggTest<-t.test(x = PaMonoMutAggSum, y = PaCoMutAggSum, paired = T)

SaMonoWtVsMutAggTest<-t.test(x = SaMonoWtAggSum, y = SaMonoMutAggSum, paired = F)
SaCoWtVsMutAggTest<-t.test(x = SaCoWtAggSum, y = SaCoMutAggSum, paired = F)
PaMonoWtVsMutAggTest<-t.test(x = PaMonoWtAggSum, y = PaMonoMutAggSum, paired = F)
PaCoWtVsMutAggTest<-t.test(x = PaCoWtAggSum, y = PaCoMutAggSum, paired = F)

tTestDataAggvsPlank<-list(SaWtAggTest, SaMutAggTest, PaWtAggTest,PaMutAggTest,SaMonoWtVsMutAggTest,SaCoWtVsMutAggTest,PaMonoWtVsMutAggTest,PaCoWtVsMutAggTest)
TtestTable<-name <- function(dataPoint) {
  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
}
tTestDataTable<-bind_rows(map(tTestDataAggvsPlank, TtestTable))
#so, it turns out I only had to do either agg or plank since the variance is the same. COOL...

@@

#MixedAggregateFrequencyPlot<-
  ggplot()+
  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentAggs ),size=1)+
  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanAggs, shape = Strain.x),size=3)+
  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanAggs-SEAggs, ymax =MeanAggs+SEAggs),size=.2, width = .2)+
  #labs(title ="Proportion of mixed species biomass")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
                     labels = c(bquote(paste(" wild-type")),
                                bquote(paste(italic(Delta*"pqsL")))))+
  labs(y = "% mixed aggregates", x = "")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")

>>>>

#now I have to do some t-tests, since I used the same cultures for mono and co for each replicate, paired t-tests are allowed.
##### 
#I know this sucks, but it's 1 AM so idgaf
SaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaMonoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaMonoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)

SaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
SaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)

#mono vs Co
SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)#wt
SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)#mutant
#Plank vs Agg
SaMonoWtAggVsPlankTest<-t.test(x = SaMonoWtAggSum, y = SaMonoWtPlankSum, paired = T)#wt
SaMonoMutAggVsPlankTest<-t.test(x = SaMonoMutAggSum, y = SaMonoMutPlankSum, paired = T)#mutant
SaCoWtAggVsPlankTest<-t.test(x = SaCoWtAggSum, y = SaCoWtPlankSum, paired = T)#wt
SaCoMutAggVsPlankTest<-t.test(x = SaCoMutAggSum, y = SaCoMutPlankSum, paired = T)#mutant
#wt vs mutant
SaMonoWtVsMutAggTest<-t.test(x = SaMonoWtAggSum, y = SaMonoMutAggSum, paired = F)
SaCoWtVsMutAggTest<-t.test(x = SaCoWtAggSum, y = SaCoMutAggSum, paired = F)

PaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
PaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
PaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
PaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)

PaMonoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
PaCoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
PaMonoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
PaCoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)

PaWtAggTest<-t.test(x = PaMonoWtAggSum, y = PaCoWtAggSum, paired = T)
PaMutAggTest<-t.test(x = PaMonoMutAggSum, y = PaCoMutAggSum, paired = T)
PaMonoWtVsMutAggTest<-t.test(x = PaMonoWtAggSum, y = PaMonoMutAggSum, paired = F)
PaCoWtVsMutAggTest<-t.test(x = PaCoWtAggSum, y = PaCoMutAggSum, paired = F)

PaMonoWtAggVsPlankTest<-t.test(x = PaMonoWtAggSum, y = PaMonoWtPlankSum, paired = T)
PaCoWtAggVsPlankTest<-t.test(x = PaCoWtAggSum, y = PaCoWtPlankSum, paired = T)
PaMonoMutAggVsPlankTest<-t.test(x = PaMonoMutAggSum, y = PaMonoMutPlankSum, paired = T)
PaCoMutAggVsPlankTest<-t.test(x = PaCoMutAggSum, y = PaCoMutPlankSum, paired = T)

tTestDataAggvsPlank<-list(SaWtAggTest,SaMutAggTest,SaMonoWtAggVsPlankTest,SaMonoMutAggVsPlankTest,
                          SaCoWtAggVsPlankTest,SaCoMutAggVsPlankTest,SaMonoWtVsMutAggTest,SaCoWtVsMutAggTest,
                          PaWtAggTest,PaMutAggTest,PaMonoWtAggVsPlankTest,PaMonoMutAggVsPlankTest,
                          PaCoWtAggVsPlankTest,PaCoMutAggVsPlankTest,PaMonoWtVsMutAggTest,PaCoWtVsMutAggTest)
TtestTable<-name <- function(dataPoint) {
  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
}
tTestDataTable<-bind_rows(map(tTestDataAggvsPlank, TtestTable))
#so, it turns out I only had to do either agg or plank since the variance is the same. COOL...

@@

#MixedAggregateFrequencyPlot<-
  ggplot()+
  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentAggs ),size=1)+
  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanAggs, shape = Strain.x),size=3)+
  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanAggs-SEAggs, ymax =MeanAggs+SEAggs),size=.2, width = .2)+
  #labs(title ="Proportion of mixed species biomass")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
                     labels = c(bquote(paste(" wild-type")),
                                bquote(paste(italic(Delta*"pqsL")))))+
  labs(y = "% mixed aggregates", x = "")+
  ylim(0,10)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
